### 2016-03-06 ch05-initvals/initial-values.tex
Comments Tom CH05: 99% verwerkt

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.8\columnwidth}
  \setlength{\figureheight}{0.6\figurewidth}
  \input{\thisDir/fig/MC-RFIR-1.11111dBSNR36pts3dB-ripple6dB.tikz}
 \caption[Model error for different initialization schemes on simulations.]{The distance $\|\model{\bullet} - \hat{G}_0 \|_2$  between the different estimates ($\model{exist}$~\legref{leg:dist-G-exist}, $\model{trunc}$~\legref{leg:dist-G-trunc} and $\model{RFIR}$~\legref{leg:dist-G-RFIR} ) and the `best theoretical' estimates ($\model{0}$) shows that the smoothers help the estimate to converge to $\model{0}$.
 The same measure is shown for the initial values $\model[init]{RFIR}$ \legref{leg:dist-G-RFIR-init} and $\model[init]{trunc}$ \legref{leg:dist-G-trunc-init}.
 $\|{G}_{0} - \hat{G}_0\|_2$\legref{leg:dist-G0} shows how far the true model and `best theoretical' estimates are apart as a reference. }
  \label{fig:single-sim}
\end{figure}

@@

To measure the transfer function, the \BK{} 1613 Filter was excited by a signal $r(t)$ and both its input $u(t)$ and output $y(t)$ were measured as shown in \figref{fig:measurementSetup}.
The output $y(t)$, however, was disturbed by a noise generator that added white noise over the frequency range $[\mathrm{DC}, 20\unit{kHz}]$.
The excitation signal $r(t)$ was white random noise with a standard deviation $\sigma_r = 0.25 \unit{V}$, consisting of $N_S = 8\,192$ samples, and sampled at $92 \unit{kHz}$.
The same noise sequence was repeated $N_R = 100$ times in succession, such that a non-parametric estimate of the noise could be obtained and the performance of the methods could be gauged over these different repetitions.
To distinguish the different repetitions, we denote the $r^{\text{th}}$ repetition of the $u$ signal as $u^{[r]}(t)$ (and similarly for $y(t)$).
The signal generation and acquisition was by means of a \gls{NI} Elvis II, using the respective \code{AO} and \code{AI} pins on the breadboard, which were wired to BNC connectors.
Although acquisition and generation were synchronized, there is a small delay $\tau = 9\unit{\mu s}$ between the acquisition of the input $u(t)$ and the output $y(t)$ due to the hardware architecture of the \gls{NI} Elvis II.
Particularly, the involved channels are captured by means of a single \gls{ADC} which is preceded by a multiplexer to select the active channel.
This obviously introduces a slight delay between the acquisition of a sample of input and output channels that is not part of system dynamics of the \BK{} filter, but rather of the experimental set-up.
As such, the output spectrum $Y(\omega)$ was multiplied by $\exp\left(-j\omega\tau \right)$ such that this inter-channel acquisition delay of the \gls{NI} Elvis is compensated, the time-domain counterpart $y(t)$ can be obtained using the \gls{IDFT}.

@@

\begin{figure}[p]
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \centering
  \ref{leg:init:stress:bodes}
  \input{\thisDir/fig/bodeplots.tikz}
  %TODO: put legend inside figure (note: subplot magic!!)
  \caption[Bode plots of the stress test filters.]{Bode plots of the tested filters~\legref{leg:bode:true} in the stress test. 
  For each filter, two (randomly selected) instanced of the parametric estimates $\model{\bullet}$ are shown per method.
  % Top to bottom: Chebyshev I, Chebyshev II, Elliptical and Butterworth characteristic.
  % Left to right: low-pass, band-pass, high-pass and band-stop.
  }
  \label{fig:bodeplots}
\end{figure}

@@

The \gls{LPM} itself solves $N$ linear systems of small dimensions ($2N_W + 1$ equations and a few degrees of freedom, i.e. $n_{\theta} \leq 2 N_W + 1$), hence the overall runtime will be $\bigO{N n_{\theta}^3}$ since solving a linear regression problem with $C$ parameters and $D$ data points takes $\bigO{C^3  + D C^2}$ operations\footnote{See http://math.stackexchange.com/questions/84495/computational-complexity-of-least-square-regression}.
The truncation of the impulse response relies on linear regression which takes $\bigO{N}$ operations since only $3$ parameters are estimated during this step.
Overall, this means that the time-truncated \gls{LPM} operates in $\bigO{N n_{\theta}^{3}}$.

@@

Whereas \gls{RFIR} is shown to provide reliable starting values, it remains advisable to have multiple initialization strategies available to improve the likelihood of attaining a good starting value.
This is also the approach that toolboxes such as \citep{FDIDENT} and \citep{TDIDENT} employ.
Luckily, trying out multiple initialization strategies is \emph{embarrassingly parallellizable}, i.e. one can easily try out a different strategy in parallel without incurring a lot of overhead in terms of wall-clock time.
As such, computing multiple starting values can happen without a significant increase in wall-clock time and consequently a sluggish user-experience.

>>>>

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.8\columnwidth}
  \setlength{\figureheight}{0.6\figurewidth}
  \input{\thisDir/fig/MC-RFIR-1.11111dBSNR36pts3dB-ripple6dB.tikz}
 \caption[Model error for different initialization schemes on simulations.]{The distance $\|\model{\bullet} - \hat{G}_0 \|_2$  between the different estimates ($\model{exist}$~\legref{leg:dist-G-exist}, $\model{trunc}$~\legref{leg:dist-G-trunc} and $\model{RFIR}$~\legref{leg:dist-G-RFIR} ) and the `best theoretical' estimates ($\model{0}$) shows that the smoothers help the estimate to converge to $\model{0}$.
 The same measure is shown for the initial values $\model[init]{RFIR}$ \legref{leg:dist-G-RFIR-init} and $\model[init]{trunc}$ \legref{leg:dist-G-trunc-init}.
 $\|{G}_{0} - \hat{G}_0\|_2$\legref{leg:dist-G0} shows how far the true model and `best theoretical' estimates are apart to put the other distances into perspective. }
  \label{fig:single-sim}
\end{figure}

@@

To measure the transfer function, the \BK{} 1613 Filter was excited by a signal $r(t)$ and both its input $u(t)$ and output $y(t)$ were measured as shown in \figref{fig:measurementSetup}.
The output $y(t)$, however, was disturbed by a noise generator that added white noise over the frequency range $[\mathrm{DC}, 20\unit{kHz}]$.
The excitation signal $r(t)$ was white random noise with a standard deviation $\sigma_r = 0.25 \unit{V}$, consisting of $N_S = 8\,192$ samples, and sampled at $92 \unit{kHz}$.
The same noise sequence was repeated $N_R = 100$ times in succession, such that a non-parametric estimate of the noise could be obtained and the performance of the methods could be gauged over these different repetitions.
To distinguish the different repetitions, we denote the $r^{\text{th}}$ repetition of the $u$ signal as $u^{[r]}(t)$ (and similarly for $y(t)$).
The signal generation and acquisition was by means of a \gls{NI} Elvis II, using the respective \code{AO} and \code{AI} pins on the breadboard, which were wired to BNC connectors.
Although acquisition and generation were synchronized, there is a small delay $\tau = 9\unit{\mu s}$ between the acquisition of the input $u(t)$ and the output $y(t)$ due to the hardware architecture of the \gls{NI} Elvis II.
Particularly, the involved channels are captured by means of a single \gls{ADC} which is preceded by a multiplexer to select the active channel.
This obviously introduces a slight delay between the acquisition of a sample of input and output channels that is not part of system dynamics of the \BK{} filter, but rather of the experimental set-up.
As such, the output spectrum $Y(\omega)$ was multiplied by $\exp\left(-j\omega\tau \right)$ such that this inter-channel acquisition delay of the \gls{NI} Elvis is compensated; the time-domain counterpart $y(t)$ is obtained using the \gls{IDFT}.

@@

\begin{figure}[p]
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \centering
  \ref{leg:init:stress:bodes}
  \input{\thisDir/fig/bodeplots.tikz}
  %TODO: put legend inside figure (note: subplot magic!!)
  \caption[Bode plots of the stress test filters.]{Bode plots of the tested filters~\legref{leg:bode:true} in the stress test. 
  For each filter, two (randomly selected) instances of the parametric estimates $\model{\bullet}$ are shown per method.
  % Top to bottom: Chebyshev I, Chebyshev II, Elliptical and Butterworth characteristic.
  % Left to right: low-pass, band-pass, high-pass and band-stop.
  }
  \label{fig:bodeplots}
\end{figure}

@@

Overall, the time-truncated \gls{LPM} operates in $\bigO{N n_{\theta}^{3}}$.
First, the \gls{LPM} solves $N$ linear systems of small dimensions ($2N_W + 1$ equations and a few degrees of freedom, i.e. $n_{\theta} \leq 2 N_W + 1$), hence the overall runtime will be $\bigO{N n_{\theta}^3}$ since solving a linear regression problem with $C$ parameters and $D$ data points takes $\bigO{C^3  + D C^2}$ operations\footnote{See http://math.stackexchange.com/questions/84495/computational-complexity-of-least-square-regression}.
The truncation of the impulse response relies on linear regression which takes $\bigO{N}$ operations since only $3$ parameters are estimated during this step.

@@

Whereas \gls{RFIR} is shown to provide reliable starting values, it remains advisable to have multiple initialization strategies available to improve the likelihood of attaining a good starting value.
This is also the approach that toolboxes such as~\citep{FDIDENT} and~\citep{TDIDENT} employ.
Luckily, trying out multiple initialization strategies is \emph{embarrassingly parallellizable}, i.e. one can easily try out a different strategy in parallel without incurring a lot of overhead in terms of wall-clock time.
As such, computing multiple starting values can happen without a significant increase in wall-clock time and consequently a sluggish user-experience.
